### 2010-12-06 report/report.tex
future work
methodology

\editbox{``we started the
  robot, and it would collect data on its own.  if it walks otusdie fo
  the viewable area, it tells us and we move it back inside and
  restart it (but the data collection continues)''}

The metric for evaluation of the designed gait is speed. We stop each 
run after plateauing results (no improvement for one third of the 
policies seen so far). The standard length of a run designates that it
should be stopped

Each algorithm was run on 3 different initial parameter vectors on the
physical robot.  ``We decided to evaluate all methods starting at the
same three vectors, to have more of a fair comparison...'' We evaluate
each method based on the amount of improvement seen from the initial
parameter vectors, and on the fastest speeds achieved during runs.

Compare to Juan's run too.

@@

\edit{Intro sentence here...}
There are several additions we would make to flesh out our project. First,
the error margins for our runs was quite large, so reducing them would lead
to more conclusive data. It would also be insightful to run our algorithms
on different motion models to get a better idea of how well different
algorithms perform overall, and not just for our current motion model. We
also intend to experiment more with evolutionary algorithms/HyperNEAT. 
Some parameter vectors resulted in the robot turning, as opposed to it
walking long distances. This could be an interesting learning goal in
future projects. To these ends, we propose the following additions
and enhancements:

>>>>

The metric for evaluation of the designed gait is speed. We stop each 
run after plateauing results (no improvement for one third of the 
policies seen so far). The standard length of a run designates that it
should be stopped after there is no improvement for one half of the policies
seen so far, but since all runs took place on the actual robot, without use
of a simulator, certain time limitations were imposed on the learning process.

We controlled our experiments from a computer that was connected via a 
wireless ethernet to the robot. The robot collected data about distance
walked automatically on its own. If it walked outside of the Wii remote's
viewable area, it informed the user, so the only human intervention
required during an experiment involved moving the robot back inside the 
viewable area and restarting it and dealing with various mechanical failures,
which did not interrupt the learning process or result in the loss of data.

We evaluated the efficacy of a set of parameters by sending these
parameters to the robot and instructing it to walk for a certain length
of time. The robot always begins from the same position and returns to the
starting position at the end of the run in order to allow for uniformity
in measuring. More efficient parameters resulted in a faster gait, which
translated into a longer distance walked and a better score. After completing
an evluation, the robot sent the resulting distance walked back to the
host computer and prepared itself for a new set of parameters to evaluate.

Each algorithm was run on 3 different initial parameter vectors on the
physical robot. We decided to evaluate all methods starting at the
same three vector in order to allow for the fair comparison of each
algorihtm.  We evaluate
each method based on the amount of improvement seen from the initial
parameter vectors, and on the fastest speeds achieved during runs.

The resulting gaits from our algorithms quickly outperformed the original
hand-coded walk designed for this robot. The fasted walk, for example, was
4 times faster.

@@

There are several additions we would make to flesh out our project. First,
the error margins for our runs was quite large, so reducing them would lead
to more conclusive data. It would also be insightful to run our algorithms
on different motion models to get a better idea of how well different
algorithms perform overall, and not just for our current motion model. We
also intend to experiment more with evolutionary algorithms/HyperNEAT. 
Some parameter vectors resulted in the robot turning, as opposed to it
walking long distances. This could be an interesting learning goal in
future projects. To these ends, we propose the following additions
and enhancements:
